Compiling refinement types to dependent types

### 2020-07-09 tex/paper.tex
It's "projections", not "accessors"
There's gonna be a bunch of concessions

Note that although the syntax does not allow refining function types or ADTs,
it does not restrict the expressive power of the language.
For instance, a refinement on a function that we might otherwise wish to write as
\[
  (x : \mathbf{Int}) \rightarrow \{ v : \mathbf{Int} \rightarrow \mathbf{Int} | v x = 0 \} \rightarrow \mathbf{Int}
\]
might instead be expressed via a dummy parameter:
\[
  (x : \mathbf{Int}) \rightarrow (f : \mathbf{Int} \rightarrow \mathbf{Int}) \rightarrow \{ \_ : \mathbf{Unit} | f x = 0 \} \rightarrow \mathbf{Int}
\]

@@

\begin{itemize}
  \item Non-dependent function type:
    \[
      \tau_1 \rightarrow \tau_2 \triangleq \Pi \_ : \tau_1. \tau_2.
    \]
  \item Dependent pair type, or $\Sigma$-type, with the first component being a value $x$ of type $\tau$ and the second component being of type $P x$:
    \[
      \{ x : \tau\ **\ P x \} \triangleq \Pi \alpha : \star. (\Pi x : \tau. P x \rightarrow \alpha) \rightarrow \alpha,
    \]
    with the corresponding accessors:
    \[
      \text{fst} \triangleq TODO,
    \]
    \[
      \text{snd} \triangleq TODO.
    \]
  \item Non-dependent pair type:
    \[
      (\tau_1, \tau_2) \triangleq \{ x : \tau_1\ **\ (\lambda \_ : \tau_1. \tau_2) x \}.
    \]
  \item Equality of expressions $\nonterm{ec}_1, \nonterm{ec}_2$ of type $S$:
    \[
      \nonterm{ec}_1 \equiv \nonterm{ec}_2 \triangleq \Pi P : S \rightarrow \star. (P x \rightarrow P y, P y \rightarrow P x).
    \]
    Careful reader will recognize this as the Leibniz equality \cite{FindSomethingForThis}.
\end{itemize}

>>>>

We also have the following concessions:
\begin{itemize}
  \item The syntax only allows refinements on base types.
    Note that this does not restrict the expressive power of the language.
    For instance, a refinement on a function that we might otherwise wish to write as
    \[
      (x : \mathbf{Int}) \rightarrow \{ v : \mathbf{Int} \rightarrow \mathbf{Int} | v x = 0 \} \rightarrow \mathbf{Int}
    \]
    might instead be expressed via a dummy parameter:
    \[
      (x : \mathbf{Int}) \rightarrow (f : \mathbf{Int} \rightarrow \mathbf{Int}) \rightarrow \{ \_ : \mathbf{Unit} | f x = 0 \} \rightarrow \mathbf{Int}.
    \]
\end{itemize}

@@

\begin{itemize}
  \item Non-dependent function type:
    \[
      \tau_1 \rightarrow \tau_2 \triangleq \Pi \_ : \tau_1. \tau_2.
    \]
  \item Dependent pair type, or $\Sigma$-type, with the first component being a value $x$ of type $\tau$ and the second component being of type $P x$:
    \[
      \{ x : \tau\ **\ P x \} \triangleq \Pi \alpha : \star. (\Pi x : \tau. P x \rightarrow \alpha) \rightarrow \alpha,
    \]
    with the corresponding projections:
    \[
      \text{fst} \triangleq TODO,
    \]
    \[
      \text{snd} \triangleq TODO.
    \]
  \item Non-dependent pair type:
    \[
      (\tau_1, \tau_2) \triangleq \{ x : \tau_1\ **\ (\lambda \_ : \tau_1. \tau_2) x \}.
    \]
  \item Equality of expressions $\nonterm{ec}_1, \nonterm{ec}_2$ of type $S$:
    \[
      \nonterm{ec}_1 \equiv \nonterm{ec}_2 \triangleq \Pi P : S \rightarrow \star. (P x \rightarrow P y, P y \rightarrow P x).
    \]
    Careful reader will recognize this as the Leibniz equality \cite{FindSomethingForThis}.
\end{itemize}
